---
title: "simpleRegress"
author: "Denise Sahagun"
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
bears$SEX<- as.factor(bears$SEX)
```

## Model LENGTH ~ NSEXTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

The residual standard error 

## now predict the length of a bear who has a neck of 17, 22 and 26



```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
AgeModel <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(AgeModel)
summary.lm(AgeModel)
```

```{r}
HeadLengthModel<- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(HeadLengthModel)
summary.lm(HeadLengthModel)
```

```{r}
HeadWidthModel <-lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(HeadWidthModel)
summary.lm(HeadWidthModel)
```

```{r}
ChestModel <-lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(ChestModel)
summary.lm(ChestModel)
```



##Summary Statement

Six separate models were developed to predict bear lengths based on other measurements and characteristics. Head length was the most accurate predictor of length. 
